\papertitle

### 2014-03-20 final-report/paper.tex
Sorry
Ref and typo

\textbf{Graph Rendering:} We use D3 \cite{d3} to render the \graph graph, which allows us to support various interactions and transistions. We use GraphViz \cite{Ellson01graphviz} in the backend to generate graph layout information. GraphViz allows us to generate graph layouts that are optimized to minimize area footprint. The layout information is then fed into a D3-based rendering engine which supports various interactions and animations techniques.

\textbf{Graph Navigation:} A query plan can be arbitrarily large. Thus we offer two mechanisms that facilitate exploration of the graph for the user: (1) expanding/reducing fragments and (2) zooming. The first mechanism can reduce the size of a graph by a constant factor by collapsing operators that compose a fragment into a single fragment node. The user can click once on a collapsed fragment to expand, and click once on an expanded fragment to collapse it. Expanding or reducing a node can cause large changes in the graph layout as GraphViz changes the graph layout to minimize overall area. This graph reshuffeling is illustrated in Figure~\ref{graph} where expanding Frag2 causes the layout to change. To address these layout changes, we implemented transitions to allow the user to track the fragments as those get reshuffled. The second mechanism that facilitates exploration of the graph for the user is zooming. This feature was implemented in D3 and allows the user to quickly jump from one part of the graph to the next, by zooming in and out of the graph view.

@@

% use the word spans when referring to events with duration (used in dapper)

>>>>

\textbf{Graph Rendering:} We use D3 \cite{2011-d3} to render the \graph graph, which allows us to support various interactions and transitions. We use GraphViz \cite{Ellson01graphviz} in the backend to generate graph layout information. GraphViz allows us to generate graph layouts that are optimized to minimize area footprint. The layout information is then fed into a D3-based rendering engine which supports various interactions and animations techniques.

\textbf{Graph Navigation:} A query plan can be arbitrarily large. Thus we offer two mechanisms that facilitate exploration of the graph for the user: (1) expanding/reducing fragments and (2) zooming. The first mechanism can reduce the size of a graph by a constant factor by collapsing operators that compose a fragment into a single fragment node. The user can click once on a collapsed fragment to expand, and click once on an expanded fragment to collapse it. Expanding or reducing a node can cause large changes in the graph layout as GraphViz changes the graph layout to minimize overall area. This graph re-shuffling is illustrated in Figure~\ref{graph} where expanding Frag2 causes the layout to change. To address these layout changes, we implemented transitions to allow the user to track the fragments as those get reshuffled. The second mechanism that facilitates exploration of the graph for the user is zooming. This feature was implemented in D3 and allows the user to quickly jump from one part of the graph to the next, by zooming in and out of the graph view.

@@

\todo{use the word spans when referring to events with duration (used in dapper)}
